\pkg{cv}: An \proglang{R} Package for Cross-Validating Regression Models

### 2024-07-14 scratch/notes_john/JSS-article/JSS-article-4.Rmd
add Georges's email address to JSS-article-4

---
documentclass: jss
author:
  - name: John Fox
    orcid: 0000-0002-1196-8012
    affiliation: 'McMaster University'
    address: |
      | Hamilton, Ontario, Canada
    email: \email{jfox@mcmaster.ca}
    url: https://www.john-fox.ca/
  - name: Georges Monette
    orcid: 0000-0003-0076-5532
    affiliation: 'York University'
    # To add another line, use \AND at the end of the previous one as above
    address: |
      | Toronto, Ontario, Canada
title:
  formatted: "\\pkg{cv}: An \\proglang{R} Package for Cross-Validating Regression Models"
  # If you use tex in the formatted title, also supply version without
  plain:     "cv: An R Package for Cross-Validating Regression Models"
  # For running headers, if needed
  short:     "\\pkg{cv}: Cross-Validating Regression Models"
abstract: >
  We describe the \pkg{cv} package, which implements cross-validation for standard \proglang{R} regression models through a uniform and simple to use generic function. Methods for the \code{cv()} function are provided for many commonly employed classes of statistical models, including mixed-effects models, and it is straightforward to extend the \pkg{cv} package by writing methods for additional classes of models. The \code{cv()} function also can cross-validate complex model-selection procedures, such as those that include variable transformations, predictor selection, and selection among competing models. The \code{cv()} function generally supports parallel computations, and the supplied methods for linear and generalized linear models take advantage of computational efficiencies.
keywords:
  # at least one keyword must be supplied
  formatted: [cross-validation, regression analysis, model selection, "\\proglang{R}"]
  plain:     [cross-validation, regression analysis, model selection, R]
preamble: >
  \usepackage{amsmath}
output: 
  rticles::jss_article:
    extra_dependencies: "subfig"
bibliography: ["cv.bib"]
---

>>>>

---
documentclass: jss
author:
  - name: John Fox
    orcid: 0000-0002-1196-8012
    affiliation: 'McMaster University'
    address: |
      | Hamilton, Ontario, Canada
    email: \email{jfox@mcmaster.ca}
    url: https://www.john-fox.ca/
  - name: Georges Monette
    orcid: 0000-0003-0076-5532
    affiliation: 'York University'
    address: |
      | Toronto, Ontario, Canada
    email: \email{georges@yorku.ca}
title:
  formatted: "\\pkg{cv}: An \\proglang{R} Package for Cross-Validating Regression Models"
  # If you use tex in the formatted title, also supply version without
  plain:     "cv: An R Package for Cross-Validating Regression Models"
  # For running headers, if needed
  short:     "\\pkg{cv}: Cross-Validating Regression Models"
abstract: >
  We describe the \pkg{cv} package, which implements cross-validation for standard \proglang{R} regression models through a uniform and simple to use generic function. Methods for the \code{cv()} function are provided for many commonly employed classes of statistical models, including mixed-effects models, and it is straightforward to extend the \pkg{cv} package by writing methods for additional classes of models. The \code{cv()} function also can cross-validate complex model-selection procedures, such as those that include variable transformations, predictor selection, and selection among competing models. The \code{cv()} function generally supports parallel computations, and the supplied methods for linear and generalized linear models take advantage of computational efficiencies.
keywords:
  # at least one keyword must be supplied
  formatted: [cross-validation, regression analysis, model selection, "\\proglang{R}"]
  plain:     [cross-validation, regression analysis, model selection, R]
preamble: >
  \usepackage{amsmath}
output: 
  rticles::jss_article:
    extra_dependencies: "subfig"
bibliography: ["cv.bib"]
---
